Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-23 paper/aldebaran.tex
misc changes

We have determined the stellar properties of Aldebaran with the additional constraint of \numax determined from our analysis here.  The details of the stellar modelling are presented in detail in \ref{sec:mod}.  We have considered the impact of our additional \numax constraint and run our analysis for different sets of spectroscopic estimates.  For final values we adopt the Sheffield et al. (2012) b spectroscopic solution as being 'middle of the road' estimates.  For the analysis without constraint on \numax we find estimates of the stellar properties as $M = 1.27^{+0.24}_{-0.2} \, \mathrm{M_{\odot}}$ and age $4.86^{+3.56}_{-2.04} \, \rm Gyr$.  With the inclusion of \numax we find $M = 1.16^{+0.07}_{-0.07} \, \mathrm{M_{\odot}}$ and age $6.38^{1.42}_{1.12} \, \rm Gyr$.  It is clear that the addition of \numax provides substantially more precise estimates of Mass and Age.

We note that with the determination of the stellar mass it is possible to infer the parameters Aldebaran had while it was on the main sequence. We conduct a Monte Carlo simulation, drawing masses randomly from a Gaussian distribution $M \sim \mathscr{N}(1.16,0.07)$ and metallicitiies $[\text{Fe}/\text{H}] \sim \mathscr{N}(-0.15,0.2)$ \citep{decin2003}  to predict the luminosity of the main-sequence progenitor, and the semi-major axis of the planet's orbit.  %Using the scaling relations of \citep{eker2015}, we find that Aldebaran would have had a luminosity $L_* = 2.0 \pm 0.37~\lsun$ on the main sequence.  
Using the Mesa Isochrones and Stellar Tracks \citep[MIST:][]{mist0,mist1}, models, we compute the luminosity and radius evolution of the planet along the main sequence. $L$ evolves from $2.0 \pm 0.7$~\lsun at 0.5~Gyr to $3.5 \pm 2.3$~\lsun at 2.5~Gyr. 
We note that this implies that the planet at a semi-major axis of $1.507 \pm 0.03$~AU would have been subject to an insolation comparable to that of the Earth, evolving from 0.5~Gyr to 2.5~Gyr from $0.86 \pm 0.27$ to $1.55 \pm 1.0$ times that of the Earth today. Subject as well as this to the great uncertainties of the planet's orbital evolution and albedo, this planet and any of its moons may well have had temperate environments for some of their previous evolution, now long-since destroyed by their host star's evolution away from the main sequence.

>>>>

We have determined the stellar properties of Aldebaran with the additional constraint of \numax determined from our analysis here.  The details of the stellar modelling are presented in detail in \ref{sec:mod}.  We have considered the impact of our additional \numax constraint and run our analysis for different sets of spectroscopic estimates.  For final values we adopt the \citet{2012Sheffield} spectroscopic solution as being `middle of the road' estimates.  For the analysis without constraint on \numax we find estimates of the stellar properties as $M = 1.27^{+0.24}_{-0.2} \, \mathrm{M_{\odot}}$ and age $4.86^{+3.56}_{-2.04} \, \rm Gyr$.  With the inclusion of \numax we find $M = 1.16^{+0.07}_{-0.07} \, \mathrm{M_{\odot}}$ and age $6.38^{1.42}_{1.12} \, \rm Gyr$.  It is clear that the addition of \numax provides substantially more precise estimates of Mass and Age.  % re sheffield - I have substituted the citation from the .bib but you said 'b'; afaik she only published one paper in 2012? - Ben

We note that with the determination of the stellar mass it is possible to infer the parameters Aldebaran had while it was on the main sequence. We conduct a Monte Carlo simulation, drawing masses randomly from a Gaussian distribution $M \sim \mathscr{N}(1.16,0.07)$ and metallicitiies $[\text{Fe}/\text{H}] \sim \mathscr{N}(-0.15,0.2)$ \citep{decin2003}  to predict the luminosity of the main-sequence progenitor, and the semi-major axis of the planet's orbit.  %Using the scaling relations of \citep{eker2015}, we find that Aldebaran would have had a luminosity $L_* = 2.0 \pm 0.37~\lsun$ on the main sequence.  
Using the Mesa Isochrones and Stellar Tracks \citep[MIST:][]{mist0,mist1} models, we compute the luminosity and radius evolution of the planet along the main sequence. $L$ evolves from $2.0 \pm 0.7$~\lsun at 0.5~Gyr to $3.5 \pm 2.3$~\lsun at 2.5~Gyr. 
We note that this implies that the planet at a semi-major axis of $1.507 \pm 0.03$~AU would have been subject to an insolation comparable to that of the Earth, evolving from 0.5~Gyr to 2.5~Gyr from $0.86 \pm 0.27$ to $1.55 \pm 1.0$ times that of the Earth today. Subject as well as this to the great uncertainties of the planet's orbital evolution and albedo, this planet and any of its moons may well have had temperate environments for some of their previous evolution, now long-since destroyed by their host star's evolution away from the main sequence.
